Subjective Experience of Demands and Resources across O*NET Job Elements

### 2024-06-06 Submission.Rmd
error message was due to `test` object (line 1111) that was renamed - we had referenced the old object within the document text

```{r}
hr_burn_info2 <- apa_print(hr_burn_m2)
hr_burn_info3 <- apa_print(hr_burn_m3)
```

@@

```{r hind-resource-table, results='asis', eval = FALSE}

@@

We also explored whether there was an interaction between hindrance stressors and resources on the outcomes (i.e., engagement, stress, and burnout). A second group of hierarchical regressions were conducted with hindrance stressors and resources added in step one of the model and an interaction term, hindrance stressors*resources, added in step two of the model. See Table \@ref(tab:ind-resource-table).

@@

Similarly, hindrance stressors and resources explained XX% of the variance in burnout, $R^2$ = .xx. Adj. $R^2$ = .xx, *F*(x, xx) = xx.xx, *p* xxx. The inclusion of the interaction term in step two of the model contributed a significant addition to the model, $\Delta R^2$ = .xx, $\Delta F$(xx, xx) = .xx, *p* = xx. The total model explained xx% of the variance in burnout,$R^2$ = .xx. Adj. $R^2$ = .xx, *F*(x, xx) = xx.xx, *p* <.xxx. Again, see Figure \@ref(fig:hind-resource-burn-int). As expected, the relationship between hindrance stressors and burnout becomes weaker as workers perceive more resources. Papaja gives us `r test$full_result`

>>>>

```{r}
hr_burn_info2 <- apa_print(hr_burn_m2)
hr_burn_info3 <- apa_print(hr_burn_m3)

@@

```{r hind-resource-table, results='asis', eval = TRUE}

@@

We also explored whether there was an interaction between hindrance stressors and resources on the outcomes (i.e., engagement, stress, and burnout). A second group of hierarchical regressions were conducted with hindrance stressors and resources added in step one of the model and an interaction term, hindrance stressors x resources, added in step two of the model. See Table \@ref(tab:hind-resource-table).

@@

Similarly, hindrance stressors and resources explained XX% of the variance in burnout, $R^2$ = .xx. Adj. $R^2$ = .xx, *F*(x, xx) = xx.xx, *p* xxx. The inclusion of the interaction term in step two of the model contributed a significant addition to the model, $\Delta R^2$ = .xx, $\Delta F$(xx, xx) = .xx, *p* = xx. The total model explained xx% of the variance in burnout,$R^2$ = .xx. Adj. $R^2$ = .xx, *F*(x, xx) = xx.xx, *p* <.xxx. Again, see Figure \@ref(fig:hind-resource-burn-int). As expected, the relationship between hindrance stressors and burnout becomes weaker as workers perceive more resources.

### 2024-06-06 Submission.tex
error message was due to `test` object (line 1111) that was renamed - we had referenced the old object within the document text

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  jou,mask]{apa7}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Subjective Experience of Demands and Resources across O*NET Job Elements},
  pdflang={en-EN},
  pdfkeywords={O*Net, challenge-hindrance framework, job demands-resources, job characteristics},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\hypertarget{the-job-demands-resources-theory-and-challenge-hindrance-stressor-framework}{%
\subsection{The Job Demands-Resources Theory and Challenge-Hindrance Stressor Framework}\label{the-job-demands-resources-theory-and-challenge-hindrance-stressor-framework}}

@@

\hypertarget{are-perceptions-of-job-resources-challenge-demands-and-hindrance-demands-universal}{%
\subsection{Are Perceptions of Job Resources, Challenge Demands, and Hindrance Demands Universal?}\label{are-perceptions-of-job-resources-challenge-demands-and-hindrance-demands-universal}}

@@

\hypertarget{connecting-appraisals-to-workplace-outcomes}{%
\subsection{Connecting Appraisals to Workplace Outcomes}\label{connecting-appraisals-to-workplace-outcomes}}

@@

\hypertarget{method}{%
\section{Method}\label{method}}

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

@@

\hypertarget{materials}{%
\subsection{Materials}\label{materials}}

@@

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

@@

\hypertarget{results}{%
\section{Results}\label{results}}

@@

Table \ref{tab:chal-resource-table} summarizes the results. Sum scores for the predictors were used here, and predictor variables were mean centered prior to running the following regressions. First exploring engagement, challenge stressors and resources explained XX\% of the variance in engagement, \(R^2\) = 0.15, Adj. \(R^2\) = 0.15 which represents a statistically significant effect, \(F(3, 564) = 9.49\), \(p < .001\). The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(\Delta R^2\) = 0.00, 2), \(\Delta F\) (1, 564) = 5.82, and thus provides statistical support for the presence of moderation. The total model explained xx\% of the variance in engagement, \(R^2\) = .xx. Adj. \(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} \textless.xxx. Figure \ref{fig:chal-resource-int} illustrates the interaction. With low levels of resources, the relationship between challenges and engagement is relatively flat and engagement is comparatively low. With more resources, the relationship between challenges and engagement is negative, but engagement still remains higher with greater reported challenge when more resources are perceived.

@@

We also explored whether there was an interaction between hindrance stressors and resources on the outcomes (i.e., engagement, stress, and burnout). A second group of hierarchical regressions were conducted with hindrance stressors and resources added in step one of the model and an interaction term, hindrance stressors*resources, added in step two of the model. See Table \ref{tab:ind-resource-table}.

@@

Similarly, hindrance stressors and resources explained XX\% of the variance in burnout, \(R^2\) = .xx. Adj. \(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} xxx. The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(\Delta R^2\) = .xx, \(\Delta F\)(xx, xx) = .xx, \emph{p} = xx. The total model explained xx\% of the variance in burnout,\(R^2\) = .xx. Adj. \(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} \textless.xxx. Again, see Figure \ref{fig:hind-resource-burn-int}. As expected, the relationship between hindrance stressors and burnout becomes weaker as workers perceive more resources. Papaja gives us \(b = 0.00\), 95\% CI \([-0.08, 0.08]\), \(t(564) = 0.00\), \(p > .999\), \(b = 0.16\), 95\% CI \([0.06, 0.26]\), \(t(564) = 3.10\), \(p = .002\), \(b = 0.03\), 95\% CI \([-0.08, 0.15]\), \(t(564) = 0.56\), \(p = .576\), \(b = -0.13\), 95\% CI \([-0.23, -0.03]\), \(t(564) = -2.63\), \(p = .009\), list(r2 = ``\(R^2 = .05\), 90\textbackslash\% CI \([0.02, 0.08]\), \(F(3, 564) = 9.49\), \(p < .001\)'')

@@

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

@@

\hypertarget{implications}{%
\subsection{Implications}\label{implications}}

@@

\hypertarget{limitations-and-future-directions}{%
\subsection{Limitations and Future Directions}\label{limitations-and-future-directions}}

@@

\hypertarget{references}{%
\section{References}\label{references}}

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-abbas2019challenge}{}}%
Abbas, M., \& Raja, U. (2019). Challenge-hindrance stressors and job outcomes: The moderating role of conscientiousness. \emph{Journal of Business and Psychology}, \emph{34}(2), 189--201.

\leavevmode\vadjust pre{\hypertarget{ref-bakker2014job}{}}%
Bakker, A. B., \& Demerouti, E. (2014). Job demands--resources theory. \emph{Wellbeing: A Complete Reference Guide}, 1--28.

\leavevmode\vadjust pre{\hypertarget{ref-bakker2017job}{}}%
Bakker, A. B., \& Demerouti, E. (2017). Job demands--resources theory: Taking stock and looking forward. \emph{Journal of Occupational Health Psychology}, \emph{22}(3), 273.

\leavevmode\vadjust pre{\hypertarget{ref-bakker2005job}{}}%
Bakker, A. B., Demerouti, E., \& Euwema, M. C. (2005). Job resources buffer the impact of job demands on burnout. \emph{Journal of Occupational Health Psychology}, \emph{10}(2), 170.

\leavevmode\vadjust pre{\hypertarget{ref-bakker2013weekly}{}}%
Bakker, A. B., \& Sanz-Vergel, A. I. (2013). Weekly work engagement and flourishing: The role of hindrance and challenge job demands. \emph{Journal of Vocational Behavior}, \emph{83}(3), 397--409.

\leavevmode\vadjust pre{\hypertarget{ref-cavanaugh2000empirical}{}}%
Cavanaugh, M. A., Boswell, W. R., Roehling, M. V., \& Boudreau, J. W. (2000). An empirical examination of self-reported work stress among US managers. \emph{Journal of Applied Psychology}, \emph{85}(1), 65.

\leavevmode\vadjust pre{\hypertarget{ref-chen2021daily}{}}%
Chen, H., Wang, H., Yuan, M., \& Xu, S. (2021). Daily challenge/hindrance demands and cognitive wellbeing: A multilevel moderated mediation model. \emph{Frontiers in Psychology}, \emph{12}, 616002.

\leavevmode\vadjust pre{\hypertarget{ref-crawford2010linking}{}}%
Crawford, E. R., LePine, J. A., \& Rich, B. L. (2010). Linking job demands and resources to employee engagement and burnout: A theoretical extension and meta-analytic test. \emph{Journal of Applied Psychology}, \emph{95}(5), 834.

\leavevmode\vadjust pre{\hypertarget{ref-demerouti2001job}{}}%
Demerouti, E., Bakker, A. B., Nachreiner, F., \& Schaufeli, W. B. (2001). The job demands-resources model of burnout. \emph{Journal of Applied Psychology}, \emph{86}(3), 499.

\leavevmode\vadjust pre{\hypertarget{ref-gerich2017relevance}{}}%
Gerich, J. (2017). The relevance of challenge and hindrance appraisals of working conditions for employees' health. \emph{International Journal of Stress Management}, \emph{24}(3), 270.

\leavevmode\vadjust pre{\hypertarget{ref-horan2020review}{}}%
Horan, K. A., Nakahara, W. H., DiStaso, M. J., \& Jex, S. M. (2020). A review of the challenge-hindrance stress model: Recent advances, expanded paradigms, and recommendations for future research. \emph{Frontiers in Psychology}, \emph{11}, 560346.

\leavevmode\vadjust pre{\hypertarget{ref-kim2020thriving}{}}%
Kim, M., \& Beehr, T. A. (2020). Thriving on demand: Challenging work results in employee flourishing through appraisals and resources. \emph{International Journal of Stress Management}, \emph{27}(2), 111.

\leavevmode\vadjust pre{\hypertarget{ref-lazarus1984stress}{}}%
Lazarus, R. S., \& Folkman, S. (1984). \emph{Stress, appraisal, and coping}. Springer publishing company.

\leavevmode\vadjust pre{\hypertarget{ref-lepine2005meta}{}}%
LePine, J. A., Podsakoff, N. P., \& LePine, M. A. (2005). A meta-analytic test of the challenge stressor--hindrance stressor framework: An explanation for inconsistent relationships among stressors and performance. \emph{Academy of Management Journal}, \emph{48}(5), 764--775.

\leavevmode\vadjust pre{\hypertarget{ref-lepine2022challenge}{}}%
LePine, M. A. (2022). The challenge-hindrance stressor framework: An integrative conceptual review and path forward. \emph{Group \& Organization Management}, \emph{47}(2), 223--254.

\leavevmode\vadjust pre{\hypertarget{ref-peterson2001understanding}{}}%
Peterson, N. G., Mumford, M. D., Borman, W. C., Jeanneret, P. R., Fleishman, E. A., Levin, K. Y., Campion, M. A., Mayfield, M. S., Morgeson, F. P., Pearlman, K., et al. (2001). Understanding work using the occupational information network (o* NET): Implications for practice and research. \emph{Personnel Psychology}, \emph{54}(2), 451--492.

\leavevmode\vadjust pre{\hypertarget{ref-pindek2024dynamic}{}}%
Pindek, S., Meyer, K., Valvo, A., \& Arvan, M. (2024). A dynamic view of the challenge-hindrance stressor framework: A meta-analysis of daily diary studies. \emph{Journal of Business and Psychology}, 1--19.

\leavevmode\vadjust pre{\hypertarget{ref-podsakoff2007differential}{}}%
Podsakoff, N. P., LePine, J. A., \& LePine, M. A. (2007). Differential challenge stressor-hindrance stressor relationships with job attitudes, turnover intentions, turnover, and withdrawal behavior: A meta-analysis. \emph{Journal of Applied Psychology}, \emph{92}(2), 438.

\leavevmode\vadjust pre{\hypertarget{ref-rodell2009can}{}}%
Rodell, J. B., \& Judge, T. A. (2009). Can {``good''} stressors spark {``bad''} behaviors? The mediating role of emotions in links of challenge and hindrance stressors with citizenship and counterproductive behaviors. \emph{Journal of Applied Psychology}, \emph{94}(6), 1438.

\leavevmode\vadjust pre{\hypertarget{ref-rosen2020challenges}{}}%
Rosen, C. C., Dimotakis, N., Cole, M. S., Taylor, S. G., Simon, L. S., Smith, T. A., \& Reina, C. S. (2020). When challenges hinder: An investigation of when and how challenge stressors impact employee outcomes. \emph{Journal of Applied Psychology}, \emph{105}(10), 1181.

\leavevmode\vadjust pre{\hypertarget{ref-searle2015merits}{}}%
Searle, B. J., \& Auton, J. C. (2015). The merits of measuring challenge and hindrance appraisals. \emph{Anxiety, Stress, \& Coping}, \emph{28}(2), 121--143.

\leavevmode\vadjust pre{\hypertarget{ref-webster2010toward}{}}%
Webster, J. R., Beehr, T. A., \& Christiansen, N. D. (2010). Toward a better understanding of the effects of hindrance and challenge stressors on work behavior. \emph{Journal of Vocational Behavior}, \emph{76}(1), 68--77.

\leavevmode\vadjust pre{\hypertarget{ref-webster2011extending}{}}%
Webster, J. R., Beehr, T. A., \& Love, K. (2011). Extending the challenge-hindrance model of occupational stress: The role of appraisal. \emph{Journal of Vocational Behavior}, \emph{79}(2), 505--516.

\leavevmode\vadjust pre{\hypertarget{ref-xanthopoulou2007job}{}}%
Xanthopoulou, D., Bakker, A. B., Dollard, M. F., Demerouti, E., Schaufeli, W. B., Taris, T. W., \& Schreurs, P. J. (2007). When do job demands particularly predict burnout? The moderating role of job resources. \emph{Journal of Managerial Psychology}, \emph{22}(8), 766--786.

\leavevmode\vadjust pre{\hypertarget{ref-R-careless}{}}%
Yentes, R. D., \& Wilhelm, F. (2021). \emph{Careless: Procedures for computing indices of careless responding}.

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  jou,mask]{apa7}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Subjective Experience of Demands and Resources across O*NET Job Elements},
  pdflang={en-EN},
  pdfkeywords={O*Net, challenge-hindrance framework, job demands-resources, job characteristics},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\subsection{The Job Demands-Resources Theory and Challenge-Hindrance Stressor Framework}\label{the-job-demands-resources-theory-and-challenge-hindrance-stressor-framework}

@@

\subsection{Are Perceptions of Job Resources, Challenge Demands, and Hindrance Demands Universal?}\label{are-perceptions-of-job-resources-challenge-demands-and-hindrance-demands-universal}

@@

\subsection{Connecting Appraisals to Workplace Outcomes}\label{connecting-appraisals-to-workplace-outcomes}

@@

\section{Method}\label{method}

\subsection{Participants}\label{participants}

@@

\subsection{Materials}\label{materials}

@@

\subsection{Procedure}\label{procedure}

@@

\section{Results}\label{results}

@@

Table \ref{tab:chal-resource-table} summarizes the results. Sum scores for the predictors were used here, and predictor variables were mean centered prior to running the following regressions. First exploring engagement, \(R^2\) = 0.15, Adj. \(R^2\) = 0.15 which represents a statistically significant effect, \(F(2, 565) = 10.68\), \(p < .001\). The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(\Delta R^2\) = 0.00, \(\Delta F\) (1, 564) = 5.82, and thus provides statistical support for the presence of moderation. The total model explained xx\% of the variance in engagement, \(F(3, 564) = 9.49\), \(p < .001\) Figure \ref{fig:chal-resource-int} illustrates the interaction. With low levels of resources, the relationship between challenges and engagement is relatively flat and engagement is comparatively low. With more resources, the relationship between challenges and engagement is negative, but engagement still remains higher with greater reported challenge when more resources are perceived.

@@

We also explored whether there was an interaction between hindrance stressors and resources on the outcomes (i.e., engagement, stress, and burnout). A second group of hierarchical regressions were conducted with hindrance stressors and resources added in step one of the model and an interaction term, hindrance stressors x resources, added in step two of the model. See Table \ref{tab:hind-resource-table}.

@@

Similarly, hindrance stressors and resources explained XX\% of the variance in burnout, \(R^2\) = .xx. Adj. \(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} xxx. The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(\Delta R^2\) = .xx, \(\Delta F\)(xx, xx) = .xx, \emph{p} = xx. The total model explained xx\% of the variance in burnout,\(R^2\) = .xx. Adj. \(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} \textless.xxx. Again, see Figure \ref{fig:hind-resource-burn-int}. As expected, the relationship between hindrance stressors and burnout becomes weaker as workers perceive more resources.

@@

\section{Discussion}\label{discussion}

@@

\subsection{Implications}\label{implications}

@@

\subsection{Limitations and Future Directions}\label{limitations-and-future-directions}

@@

\section{References}\label{references}

@@

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-abbas2019challenge}
Abbas, M., \& Raja, U. (2019). Challenge-hindrance stressors and job outcomes: The moderating role of conscientiousness. \emph{Journal of Business and Psychology}, \emph{34}(2), 189--201.

\bibitem[\citeproctext]{ref-bakker2014job}
Bakker, A. B., \& Demerouti, E. (2014). Job demands--resources theory. \emph{Wellbeing: A Complete Reference Guide}, 1--28.

\bibitem[\citeproctext]{ref-bakker2017job}
Bakker, A. B., \& Demerouti, E. (2017). Job demands--resources theory: Taking stock and looking forward. \emph{Journal of Occupational Health Psychology}, \emph{22}(3), 273.

\bibitem[\citeproctext]{ref-bakker2005job}
Bakker, A. B., Demerouti, E., \& Euwema, M. C. (2005). Job resources buffer the impact of job demands on burnout. \emph{Journal of Occupational Health Psychology}, \emph{10}(2), 170.

\bibitem[\citeproctext]{ref-bakker2013weekly}
Bakker, A. B., \& Sanz-Vergel, A. I. (2013). Weekly work engagement and flourishing: The role of hindrance and challenge job demands. \emph{Journal of Vocational Behavior}, \emph{83}(3), 397--409.

\bibitem[\citeproctext]{ref-cavanaugh2000empirical}
Cavanaugh, M. A., Boswell, W. R., Roehling, M. V., \& Boudreau, J. W. (2000). An empirical examination of self-reported work stress among US managers. \emph{Journal of Applied Psychology}, \emph{85}(1), 65.

\bibitem[\citeproctext]{ref-chen2021daily}
Chen, H., Wang, H., Yuan, M., \& Xu, S. (2021). Daily challenge/hindrance demands and cognitive wellbeing: A multilevel moderated mediation model. \emph{Frontiers in Psychology}, \emph{12}, 616002.

\bibitem[\citeproctext]{ref-crawford2010linking}
Crawford, E. R., LePine, J. A., \& Rich, B. L. (2010). Linking job demands and resources to employee engagement and burnout: A theoretical extension and meta-analytic test. \emph{Journal of Applied Psychology}, \emph{95}(5), 834.

\bibitem[\citeproctext]{ref-demerouti2001job}
Demerouti, E., Bakker, A. B., Nachreiner, F., \& Schaufeli, W. B. (2001). The job demands-resources model of burnout. \emph{Journal of Applied Psychology}, \emph{86}(3), 499.

\bibitem[\citeproctext]{ref-gerich2017relevance}
Gerich, J. (2017). The relevance of challenge and hindrance appraisals of working conditions for employees' health. \emph{International Journal of Stress Management}, \emph{24}(3), 270.

\bibitem[\citeproctext]{ref-horan2020review}
Horan, K. A., Nakahara, W. H., DiStaso, M. J., \& Jex, S. M. (2020). A review of the challenge-hindrance stress model: Recent advances, expanded paradigms, and recommendations for future research. \emph{Frontiers in Psychology}, \emph{11}, 560346.

\bibitem[\citeproctext]{ref-kim2020thriving}
Kim, M., \& Beehr, T. A. (2020). Thriving on demand: Challenging work results in employee flourishing through appraisals and resources. \emph{International Journal of Stress Management}, \emph{27}(2), 111.

\bibitem[\citeproctext]{ref-lazarus1984stress}
Lazarus, R. S., \& Folkman, S. (1984). \emph{Stress, appraisal, and coping}. Springer publishing company.

\bibitem[\citeproctext]{ref-lepine2005meta}
LePine, J. A., Podsakoff, N. P., \& LePine, M. A. (2005). A meta-analytic test of the challenge stressor--hindrance stressor framework: An explanation for inconsistent relationships among stressors and performance. \emph{Academy of Management Journal}, \emph{48}(5), 764--775.

\bibitem[\citeproctext]{ref-lepine2022challenge}
LePine, M. A. (2022). The challenge-hindrance stressor framework: An integrative conceptual review and path forward. \emph{Group \& Organization Management}, \emph{47}(2), 223--254.

\bibitem[\citeproctext]{ref-peterson2001understanding}
Peterson, N. G., Mumford, M. D., Borman, W. C., Jeanneret, P. R., Fleishman, E. A., Levin, K. Y., Campion, M. A., Mayfield, M. S., Morgeson, F. P., Pearlman, K., et al. (2001). Understanding work using the occupational information network (o* NET): Implications for practice and research. \emph{Personnel Psychology}, \emph{54}(2), 451--492.

\bibitem[\citeproctext]{ref-pindek2024dynamic}
Pindek, S., Meyer, K., Valvo, A., \& Arvan, M. (2024). A dynamic view of the challenge-hindrance stressor framework: A meta-analysis of daily diary studies. \emph{Journal of Business and Psychology}, 1--19.

\bibitem[\citeproctext]{ref-podsakoff2007differential}
Podsakoff, N. P., LePine, J. A., \& LePine, M. A. (2007). Differential challenge stressor-hindrance stressor relationships with job attitudes, turnover intentions, turnover, and withdrawal behavior: A meta-analysis. \emph{Journal of Applied Psychology}, \emph{92}(2), 438.

\bibitem[\citeproctext]{ref-rodell2009can}
Rodell, J. B., \& Judge, T. A. (2009). Can {``good''} stressors spark {``bad''} behaviors? The mediating role of emotions in links of challenge and hindrance stressors with citizenship and counterproductive behaviors. \emph{Journal of Applied Psychology}, \emph{94}(6), 1438.

\bibitem[\citeproctext]{ref-rosen2020challenges}
Rosen, C. C., Dimotakis, N., Cole, M. S., Taylor, S. G., Simon, L. S., Smith, T. A., \& Reina, C. S. (2020). When challenges hinder: An investigation of when and how challenge stressors impact employee outcomes. \emph{Journal of Applied Psychology}, \emph{105}(10), 1181.

\bibitem[\citeproctext]{ref-searle2015merits}
Searle, B. J., \& Auton, J. C. (2015). The merits of measuring challenge and hindrance appraisals. \emph{Anxiety, Stress, \& Coping}, \emph{28}(2), 121--143.

\bibitem[\citeproctext]{ref-webster2010toward}
Webster, J. R., Beehr, T. A., \& Christiansen, N. D. (2010). Toward a better understanding of the effects of hindrance and challenge stressors on work behavior. \emph{Journal of Vocational Behavior}, \emph{76}(1), 68--77.

\bibitem[\citeproctext]{ref-webster2011extending}
Webster, J. R., Beehr, T. A., \& Love, K. (2011). Extending the challenge-hindrance model of occupational stress: The role of appraisal. \emph{Journal of Vocational Behavior}, \emph{79}(2), 505--516.

\bibitem[\citeproctext]{ref-xanthopoulou2007job}
Xanthopoulou, D., Bakker, A. B., Dollard, M. F., Demerouti, E., Schaufeli, W. B., Taris, T. W., \& Schreurs, P. J. (2007). When do job demands particularly predict burnout? The moderating role of job resources. \emph{Journal of Managerial Psychology}, \emph{22}(8), 766--786.

\bibitem[\citeproctext]{ref-R-careless}
Yentes, R. D., \& Wilhelm, F. (2021). \emph{Careless: Procedures for computing indices of careless responding}.
